\section{Large scale test using a pH-indicator and sodium hydroxide}

\subsection{Background}
From the beginning it had been suggested by SpinChem\textsuperscript{\textregistered} that a large scale test with the finished product should take place. The test was supposed to be performed using water resembling that of a mining pond with all of its usual pollutants. The vehicle should, in this volume, be manoeuvred while carrying one or more RBRs loaded with a suitable material. A suitable material would be one that is capable of adsorbing the pollutents of interest.

After reconsideration, SpinChem\textsuperscript{\textregistered} decided it would be a bad idea to create a larger volume of heavy metal polluted water. In the case that it could not be fully recovered, it would be both tedious and expensive to dispose of the polluted water. The volume for the large scale experiment was set to be 2 m$^3$.

\subsection{Method}
Instead of using polluted water it was suggested to perform a simpler, more environmental, visual test using either a coloring agent called allura red, and purify it by loading the RBR with active carbon (AC). This process would color the water red, and when the colored water is forced through the rotating RBR, the allura red would slowly be adsorbed by the AC, making it less red as more and more water gets treated. This process would take a considerable amount of time, but in return it has the benefit of restoring the water to practically the inital conditions as it were before adding the allura red.
 
The other alternative would be to use the pH-indicator phenolphthalein in combination with a base (NaOH) which would dye the water pink when the pH gets above 8. For the test with the phenolphthalein the reactor chambers would be loaded with cation-exchange resins amberlite (CER). The phenolphthalein would be added to the 2 m$^3$ of water. This by itself would however not induce a change of color in the water. Only when adding enough NaOH to force the pH above 9, the phenolphthalein would give off a pink color. The CER in the RBR would neutralize the base until the pH drops below 9, and thereby shifting the color of the water back to colorless. This process would not require the full volume of water to be treated by the RBR, it would only require that enough particles, in the total voulume, is adsorbed by the CER in order to lower the pH below 8 in the total volume. The concerns when using the CER approach would be the amounts of phenolphthalein required for reflecting a strong enough coloring in the final volume, since the phenolphthalein itself will not be adsorbed.

Compared to the AC process this method is very fast. However the water will not be completly restored after just neutralizing the NaOH. Since the phenolphthalein does not get adsorbed itself, it is necessary to inspect whether or not phenolphthalein would be okay to dispose of in regular sewers. It turned out that phenolphthalein poses no danger as a marine pollutant\cite{url}, all the same it would be best to use as little as possible.
After careful considerations, it was decided to perform the large scale test using the CER approach.

\subsection{Experimental set up}
A fixed volume of 150~ml distilled water, mixed with a fixed amount of 150~$\mu$l 1~M NaOH was prepared before each run. The start concentration of phenolphthalein in the prepared mixture was set to $0.05$~mg/l. For each new testrun the concentration was halved until the pink color no longer appeared before the naked eye. The final concentration of phenolphthalein needed was a mere $0.78$~percent of the start concentration. To scale up to the final volume of 2~m$^3$ it would only require $0.78$~g of pure phenolphthalein. The final concentration would be $1.225$~$\mu$M (see \cref{sec:calculations}).

With a known minimum concentration of phenolphthalein required, the process of minimizing the amount of needed NaOH could begin. A fixed concentration of phenolphthalein ($0.78$~percent of $0.05$~mg/ml) was mixed in 150~ml of distilled water. For the first test 150~$\mu$l of 1 Molar NaOH was added. For each iteration, the amount of NaOH was lowerd, until no pink color could be observed.  Scaling up to the final volume of 2~m$^3$ revealed that it would require $3.5$~L of 1~M NaOH for the final test.

\subsection{Distilled water Vs. tapwater}
Since all the minor tests had been performed using distilled water rather than tap water, which would be used in the large scale test, there was a need to redo the previous experiments with tap water. When testing the amounts of NaOH needed, it seemed as though it required more NaOH the first time, compared to rest of the runs. To avoid wasting phenolphthalein, the same water was used for the following test, with the only differences that a RBR loaded with CER had been used in between to neutralize the NaOH.

The theory behind needing more NaOH the first time is simply that the initial pH of the mixture, of water and phenolftalein, is lower than the shifting point for the phenolfthalein. Meaning that the first test had an initial pH around 6-7 while the later tests starts at the shifting point of the phenolfthalein at pH of 8-9, thus requiring less NaOH compared to the first test.
Comparing the pH between distilled water and tapwater showed that distilled water had somewhat lower pH initially. Also, after running the CER loaded RBRs without any added base, there was a slight decrease in pH for both distilled water and tapwater. The decrease was however larger in tapwater when comparing to their respective initial pH.
The new test showed that it would require a small increase of phenolphthalein from $0.78$~g up to $1.17$~g. The NaOH was increased by a tenfold.

\subsection{Scaling up}
When testing in larger scales of 5~L and 70~L it became clear that the amount of base needed, in order to visually detect a pink color, decreased exponentially. When testing with 70~L it only required 20~ml instead of the expected 120~ml (calculated from the 150~ml experiments).

In the final volume of 2~m$^3$ it only required 150~ml of 1~M NaOH to turn the entire volume pink. This can be explained by Lamberts law which explains that there is an exponential correlation between the transmission of light through a substance, the product of the absorption and the length the light passes through the material.\cite{pierre}

\subsection{Calculations}\label{sec:calculations}
The first calculations for phenolphthalein using distilled water:
$1.17$~ml of $0.05$~mg/ml phenolphthalein was needed in a total volume of $0.150$~L:
\begin{equation}\label{eq:concentration}
    1.17 \text{ ml} \times 0.05 \text{ mg/ml}
    = 0.0585 \text{ mg} = 0.0000585 \text{ g} \text{ phenolphthalein per } 0.150 \text{ ml}.
\end{equation}

The final volume is $2000$~dm$^3$, upscaling from $0.150$~dm$^3$:
\begin{align}
x \times 0.150 \text{ dm}^3 &= 2000 \text{ dm}^3 \nonumber \\
x &= \frac{2000 \text{ dm}^3}{0.150 \text{ dm}^3} \approx 13333.33 \\
0.00117 \text{ L} \times 13333.33 &\approx 15.6 \text{ L phenolphthalein.} 
\end{align}
For the final volume of 2000~dm$^3$, there should be $15.6$~L of the $0.05$~mg/ml phenolphthalein solution.
To simplify it is practical to recalculate this into how many grams of the substance we need instead:
\begin{equation}
    15.6 \text{ L} \times 0.05 \text{ mg/ml} = 0.78 \text{ g}.
\end{equation}

To put this in concentrations for the final volume of 2000~dm$^3$:

\begin{align}
    \text{volume } V &= 2000 \text{ dm}^3 \\
    \text{molarmass phenolftalein } M_p &= 318.3228 \text{ g/mol} \\
    \text{mass } m &= 0.78 \text{ g} \\
    \text{moles } M &= \frac{0.78 \text{ g}}{318.3228 \text{ g/mol}} \approx 0.00245 \text{ mol} \\
    \text{concentration } c &= n/V = 0.000001225 \text{ mol/dm}^3 = 1.225 \mu\text{M}
\end{align}

The final amount of phenolphthalein used was calculated in the same manner as described above where the only difference was that ,instead of using $1.17$~ml of the $0.05$~mg/ml phenolphthalein solution, $1.755$~ml was used.
This implies that the final concentrations increased as well but it is still in the vicinity of a few $\mu$M.

For the NaOH the calculations are not really important since most of the time it was just to pour until the water-mass started taking a pinkish color. The amounts changed drastically with every upscale performed. In the end it only required 150~$\mu$l 1~M NaOH to color 2000~dm$^3$.

\subsection{Results and discussion}
After performing a few test runs, and adjusting the amount of NaOH, we managed to reduce the time needed to decolor the 2~m$^3$ water from 25 to 10~minutes. The floating platform carrying two rotating RBRs loaded with CER was successfully manoeuvred around the pool. During the test it was clearly visible how the water just beneath the platform, around the RBRs, lost its pink color.
We had guessed in advance that it would take up to 45-60 minutes to decolor the large volume. The fact that it only took 10~minutes was beyond expectations. If given more time it would have been interesting to perform a large scale test, using naturally heavy metal polluted water, with the adsorbtion material that performed best (goethite) in the adsorbtion material experiments. 

\subsection{Conclusion}
The SpinChem\textsuperscript{\textregistered}'s patterned RBR can be put on floating constructions and be remotely manoeuvred in order to purify larger volumes of polluted water. This can also be done within reasonable time frames. These tests supports the possibility to load the reactors with other materials in order to specifically adsorb certain kinds of pollutants. It clearly has the potential to purify larger volumes of polluted water without having a negative effect on the environment.
